cvx-flats

### 2020-05-19 neurips-20/cvx-flats-statements.tex
Simplified proofs and tightened up

	We simply say the pair is consistent with respect to $\gamma$ if there is a distance $\mu^\gamma$ such that $(L,\psi)$ are $\mu$-consistent with respect to $\gamma$.
\end{definition}

\jessie{Should this also be a lemma instead of a proposition?}
\begin{proposition}\label{prop:consistent-implies-calibrated}
	If a (continuous) loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
	\jessiet{Probably appendix later.}
\end{proposition}
\begin{proof}
	\jessie{Contrapositive.
		Not calibrated means there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
		Take $D = D_x = p$ for some $x \in \X$, and any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$. 
		Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi(f(X)), Y) \not \to \inf_f \E_D \ell(\psi(f(X)), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$. 
	}

	Let $\gamma$ be the property elicited by $\ell$.
	Suppose $(L,\psi)$ is not calibrated with respect to $\ell$; we will show they are not consistent with respect to $\ell$ either.
	$(L, \psi)$ not calibrated with respect to $\ell$ means that there is some distribution $p \in \simplex$ such that there is no function $\zeta : \reals_+ \to \reals_+$ with $\zeta(0) = 0$ and continuous at $0^+$ such that, for all $u \in \reals^d$, we have $\ell(\psi(u); p) - \risk{\ell}(p) \leq \zeta(L(u;p) - \risk{L}(p))$. 
	In other words, for all $\zeta$ satisfying the assumptions, we have $\ell(\psi(u); p) - \risk{\ell}(p) > \zeta(L(u;p) - \risk{L}(p))$ for some $u \in \reals^d$.
	In particular, there must exist a sequence $\{u_m\}$ so that $L(u_m;p) \to \risk{L}(p)$.

	Now consider the data distribution $D$ that has a point mass on some $x \in \X$, where $p = D_x$.
	Moreover, let $f_m$ be any sequence of functions with $f_m(x) = u_m$ for all $m$.
	We then have $L(f_m(x); p) = L(u_m; p) \to \risk{L}(p)$, so $\lim_{m \to \infty}\zeta(L(u_m;p) - \risk{L}(p)) \to 0$.
	This gives $\ell(\psi(u_m);p) > \risk{\ell}(p) + \epsilon_m$ for all $m$, and $\epsilon_m \to 0$.
	We can now observe that we do not have consistency as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$.
	Therefore, if $(L, \psi)$ are consistent with respect to $\ell$, they are also calibrated with respect to $\ell$.
\end{proof}

\begin{lemma}\label{lem:calib-implies-indir}
	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
	As $p \in \Gamma_u$, then $\zeta(L(u;p) - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \ell(\gamma(p); p)$.
	We also have $\ell(\psi(u); p) \geq \risk{\ell}(p)$ by definition of $\risk{\ell}$, so we must have $\ell(\psi(u);p) = \risk{\ell}(p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
	Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
\end{proof}

\begin{lemma}\label{lem:consistent-loss-implies-prop}
	If $(L, \psi)$ are consistent with respect to $\ell$, then they are consistent with respect to $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	Define $\mu^\gamma(r, p) := R_\ell(r;p)$.
	Now suppose 
	\jessie{TODO}
\end{proof}

@@

	We show the contrapositive; suppose $(L, \psi)$ is not consistent with respect to $\gamma$, and take $\Gamma := \prop{L}$.
	Then there is a distribution $p \in \simplex$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$.
	Consider the constant sequence $\{u_m\} = u$ for all $m$.

	We then consider a distribution $D = D_x = p$ for some $x \in \X$ and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
	This yields $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$ since $u \in \Gamma(p)$.
	However, we have $\mu(\psi(u_m), \gamma(p)) \not \to 0$ as $\mu(\psi(u), \gamma(p)) \neq 0$, since $\psi(u) \not \in \gamma(p)$ and the sequence is constant.
	Hence, we do not have consistency.
\end{proof}

@@

\begin{proposition}
	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ and $\gamma:= \prop{\ell}$.
	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
	\jessie{Need to define $\eliccvx$ and $\ccdim$.}
\end{proposition}
\begin{proof}
	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
	Then $L$ indirectly elicits $\gamma$.
\end{proof}

@@

Consider the following four conditions:
\begin{enumerate}
	\item [A] $\zeta:\reals \to \reals_+$ satisfies $\zeta : 0 \mapsto 0$ and is continuous at $0$.
	\item [B] $\epsilon_m \to 0 \implies \zeta(\epsilon_m) \to 0$.
	\item [C] For all $u \in \reals^d$, $R_\ell(\psi(u); p) \leq \zeta(R_L(u;p))$.
	\item [D] For all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
\end{enumerate}

\begin{proposition}
	When $\R$ is finite and $L$ continuous in $\reals^d$, calibration of a property via Definition~\ref{def:calibrated-general} implies calibration via Definition~\ref{def:calibrated-finite}.
	\jessie{eventually want iff}
\end{proposition}
\begin{proof}
	\jessie{Contrapositive; not calibration by def~\ref{def:calibrated-finite} implies $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_u L(u; p)$.
	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.  Now we contradict $D$ and by Lemma~\ref{lem:calib-converging-regrets}, we have not calibrated by Def~\ref{def:calibrated-general}. }

	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.

	Suppose there was a distribution $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.
	There must then be a sequence $\{u_m\} \to u$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.

	This consequently implies $R_L(u_m;p) \to 0$ as $L(u_m; p) \to \risk{L}(p)$, but as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$ (if it did converge, then we would have $\psi(u_m) \to r \in \gamma(p)$), so $R_\ell(\psi(u_m); p) \not \to 0$.
	Thus, by Lemma~\ref{lem:calib-converging-regrets}, we have no calibration via Definition~\ref{def:calibrated-general}.

%	We want to show that there is no $\zeta:\reals_+ \to \reals_+$ continuous at $0^+$ with $\zeta(0) = 0$ so that 
%	\begin{align*}
%	\ell(\psi(u);p) - \risk{\ell}(p) \leq \zeta(L(u;p) - \risk{L}(p))
%	\end{align*}
%	for all $u \in \reals^d$.
%	We show that if this bound is satisfied, one of the two conditions on $\zeta$ (continuity at $0^+$ and $\zeta(0) = 0$) must be violated.
%	
%	
%	First, suppose that $\zeta$ is continuous at $0^+$ and the bound is satisfied.
%	Then for the sequence $\{u_m\} \to \Gamma(p)$, we have 
%	\begin{align*}
%	\lim_{m \to \infty}\ell(\psi(u_m); p) - \risk{\ell}(p)&\leq \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p))\\
%%	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \risk{\ell}(p) + \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p)\\
%	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \risk{\ell}(p) + \lim_{\epsilon \to 0^+} \zeta(\epsilon)~.~
%	\end{align*}
%	As $\lim_{m \to \infty} \ell(\psi(u_m);p) > \risk{\ell}(p)$, the last inequality can only happen if $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$, and by continuity of $\zeta$ at $0^+$, we must then have $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = \zeta(0) = c > 0$.

@@

\begin{lemma}\label{lem:continuous-iff-limits}
	A function $\zeta:\reals \to \reals$ is continuous at $0$ and $\zeta(0) = 0$ if and only if the sequence $\{u_m\} \to 0 \implies \zeta(u_m) \to 0$.
\end{lemma}
\begin{proof}
	$\implies$ Suppose we have a sequence $\{u_m\} \to 0$.
	By continuity, we have $\lim_{u_m \to 0}\zeta(u_m) = \zeta(0) = 0$, so $\zeta(u_m) \to 0$.

@@

\begin{lemma}\label{lem:calib-converging-regrets}
	A continuous surrogate and link $(L,\psi)$ are calibrated (via definition~\ref{def:calibrated-general}) with respect to $\ell$ if and only if, for all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
\end{lemma}
\begin{proof}
	$\implies$ Take a sequence $\{u_m\}$ so that $R_L(u_m;p) \to 0$.
	Since $\zeta(0) = 0$ and $\zeta$ is continuous at $0$, $\zeta(R_L(u_m;p)) \to 0$ by calibration.
	As regret is nonnegative, we then have $R_\ell(\psi(u_m); p) \to 0$

@@

	\jessie{Outline: 1. $\zeta$ satisfies requirements (A).  2. Verify bound is true elsewhere by construction of $\zeta$.}

	First, we can verify that $\zeta$ as constructed is continuous at $0$ and $\zeta(0) = 0$.
	As $c < 0 \implies \lim_{c \to 0^-} \zeta(c) = 0$, we need to show first that $\lim_{c \to 0^+} \zeta(c) = 0$ and $\zeta(0) = 0$.
	Consider $\{u_m\}$ so that $R_L(u_m;p) \to 0$. Since $R_\ell(\psi(u_m); p) \to 0$, we have the supremum of a function continuous (at $0^+$) is also continuous at $0^+$, so we have $\lim_{c \to 0^+} \zeta(c) = 0$.

	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, taking any $\{u_m\} \to u \in \Gamma(p)$ yields $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \lim_{m \to \infty} R_\ell(\psi(u_m); p) = 0$, with equality following since $\{u_m\}$ is arbitrary. \jessie{Not super happy with this, but I also think I'm making it more complicated than it needs to be.}

	Second, we want to verify that the bound in Equation~\ref{eq:calibrated-general} holds as regrets approach $0$.
	Fix $p \in \simplex$.
	If $\{u_m\}$ is a sequence so that $R_L(u_m; p) \to 0$, then $\zeta(R_L(u_m; p)) \to 0$.
	As $R_\ell(\psi(u_m); p) \to 0$, then $\zeta$ of surrogate regret upper bounds discrete regret as surrogate regret gets arbitrarily close to $0$.

	Last, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for $\{u_m\} \not \to 0$ by construction of $\zeta$.

	Suppose $R_\ell(\psi(u);p) = c$.
	For all $u \in \reals^d$, calibration via $\zeta$ yields $R_\ell(\psi(u);p) \leq \sup_{u' : R_L(u';p) \leq R_L(u,p)} R_\ell(\psi(u') ; p)$.
	As $u$ is in the space of the supremum ($R_L(u;p) \leq R_L(u;p)$), we then have calibration by definition of the supremum.
\end{proof}

>>>>

	We simply say the pair is consistent with respect to $\gamma$ if there is a $\mu^\gamma$ such that $(L,\psi)$ are $\mu$-consistent with respect to $\gamma$.
\end{definition}

\begin{proposition}\label{prop:consistent-implies-calibrated}
	If a (continuous) loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
\end{proposition}
\begin{proof}
%	\jessie{Intuition: Contrapositive.
%		Not calibrated means there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
%		Take $D = D_x = p$ for some $x \in \X$, and any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$. 
%		Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi(f(X)), Y) \not \to \inf_f \E_D \ell(\psi(f(X)), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$. 
%	}

	We show the contrapositive.
	If $(L, \psi)$ are not calibrated with respect to $\ell$, then there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
	Take $D = D_x = p$ for some $x \in \X$, and any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$. 
	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi(f(X)), Y) \not \to \inf_f \E_D \ell(\psi(f(X)), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.

% Commented 05.19.2020 to simplify with proof of lemma~\ref{lem:calib-converging-regrets}.
%	Let $\gamma$ be the property elicited by $\ell$.
%	Suppose $(L,\psi)$ is not calibrated with respect to $\ell$; we will show they are not consistent with respect to $\ell$ either.
%	$(L, \psi)$ not calibrated with respect to $\ell$ means that there is some distribution $p \in \simplex$ such that there is no function $\zeta : \reals_+ \to \reals_+$ with $\zeta(0) = 0$ and continuous at $0^+$ such that, for all $u \in \reals^d$, we have $\ell(\psi(u); p) - \risk{\ell}(p) \leq \zeta(L(u;p) - \risk{L}(p))$. 
%	In other words, for all $\zeta$ satisfying the assumptions, we have $\ell(\psi(u); p) - \risk{\ell}(p) > \zeta(L(u;p) - \risk{L}(p))$ for some $u \in \reals^d$.
%	In particular, there must exist a sequence $\{u_m\}$ so that $L(u_m;p) \to \risk{L}(p)$.
%	
%	
%	Now consider the data distribution $D$ that has a point mass on some $x \in \X$, where $p = D_x$.
%	Moreover, let $f_m$ be any sequence of functions with $f_m(x) = u_m$ for all $m$.
%	We then have $L(f_m(x); p) = L(u_m; p) \to \risk{L}(p)$, so $\lim_{m \to \infty}\zeta(L(u_m;p) - \risk{L}(p)) \to 0$.
%	This gives $\ell(\psi(u_m);p) > \risk{\ell}(p) + \epsilon_m$ for all $m$, and $\epsilon_m \to 0$.
%	We can now observe that we do not have consistency as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$.
%	Therefore, if $(L, \psi)$ are consistent with respect to $\ell$, they are also calibrated with respect to $\ell$.
\end{proof}

\begin{lemma}\label{lem:calib-implies-indir}
	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
	As $p \in \Gamma_u$, then $\zeta(L(u;p) - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
	We also have $\ell(\psi(u); p) \geq \risk{\ell}(p)$ by definition of $\risk{\ell}$, so we must have $\ell(\psi(u);p) = \risk{\ell}(p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
	Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
\end{proof}

\begin{lemma}\label{lem:consistent-loss-implies-prop}
	If $(L, \psi)$ are consistent with respect to $\ell$, then they are consistent with respect to $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	Define $\mu^\gamma(r, p) := R_\ell(r;p)$.
	First, observe that $\mu^\gamma(r,p) = 0 \iff r \in \gamma(p)$, since $r \in \gamma(p)$ implies $\ell(r;p) = \risk{\ell}(p)$, and if $r \not \in \gamma(p)$, then $\ell(r;p) > \risk{\ell}(p)$.

	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ so that, for all $D$ over $\X \times \Y$, we have $\E_D L(f_m(X)) \to \inf_f \E_D L(f(X), Y)$.
	This implies 
	\begin{align*}
	&\; \E_D \ell(\psi(f_m(X)), Y)\to \inf_f \E_D \ell(\psi(f(X)), Y) \\
	&\iff \E_D \ell(\psi(f_m(X)), Y) - \inf_f \ell(\psi(f(X)), Y) \to 0 \\
	&\implies \E_X R_\ell(\psi(f_m(X)), D_X) \to 0~.~
	\end{align*}
	As regret defines $\mu^\gamma$ and tends to $0$, we observe consistency with respect to $\gamma$.
\end{proof}

@@

	We show the contrapositive; suppose $(L, \psi)$ does not indirectly elicit $\gamma$, and take $\Gamma := \prop{L}$.
	Then there is a distribution $p \in \simplex$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$.

	Consider the constant sequence $\{u_m\} = u$ for all $m$, a distribution $D$ with point mass on $x$ and $D_x = p$, and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
	This yields $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$ since $u \in \Gamma(p)$.
	However, we have $\mu(\psi(u_m), \gamma(p)) \not \to 0$ as $\mu(\psi(u), \gamma(p)) \neq 0$ (since $\psi(u) \not \in \gamma(p)$) and the sequence is constant.
	Thus, we do not have consistency.
\end{proof}

@@

\begin{proposition}
	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ and $\gamma:= \prop{\ell}$.
	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
	\jessie{Need to define $\eliccvx$ and $\ccdim$.}
\end{proposition}
\begin{proof}
	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.
\end{proof}

@@

\jessie{Consider the following four conditions:
\begin{enumerate}
	\item [A] $\zeta:\reals \to \reals_+$ satisfies $\zeta : 0 \mapsto 0$ and is continuous at $0$.
	\item [B] $\epsilon_m \to 0 \implies \zeta(\epsilon_m) \to 0$.
	\item [C] Given $\zeta:\reals \to \reals_+$, for all $u \in \reals^d$, $R_\ell(\psi(u); p) \leq \zeta(R_L(u;p))$.
	\item [D] For all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
\end{enumerate}
$(A \wedge C)$ define calibration, and we have $A \iff B$ in shown in Lemma~\ref{lem:continuous-iff-limits}.  Lemma~\ref{lem:calib-converging-regrets} shoes calibration iff $D$.}

\begin{proposition}
	When $\R$ is finite and $L$ continuous in $\reals^d$, calibration via Definition~\ref{def:calibrated-general} implies calibration via Definition~\ref{def:calibrated-finite}.
	\jessie{eventually want iff}
\end{proposition}
\begin{proof}
	\jessie{Old proof commented out; simplified using Lemma~\ref{lem:calib-converging-regrets}}

	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_u L(u; p)$.
	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.  
	Now we have $R_L(u_m; p \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, so by Lemma~\ref{lem:calib-converging-regrets}, we contradict calibration by Def~\ref{def:calibrated-general}.

% Commented out 05.19.2020 for easier proof if Lemma 5 is true.
%	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
%	
%	Suppose there was a distribution $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.
%	There must then be a sequence $\{u_m\} \to u$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.
%	
%	This consequently implies $R_L(u_m;p) \to 0$ as $L(u_m; p) \to \risk{L}(p)$, but as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$ (if it did converge, then we would have $\psi(u_m) \to r \in \gamma(p)$), so $R_\ell(\psi(u_m); p) \not \to 0$.
%	Thus, by Lemma~\ref{lem:calib-converging-regrets}, we have no calibration via Definition~\ref{def:calibrated-general}.

@@

\begin{lemma}\label{lem:continuous-iff-limits}
	A function $\zeta:\reals \to \reals$ is continuous at $0$ and $\zeta(0) = 0$ if and only if the sequence $\{u_m\} \to 0 \implies \zeta(u_m) \to 0$.
	\jessie{$A \iff B$}
\end{lemma}
\begin{proof}
	$\implies$ Suppose we have a sequence $\{u_m\} \to 0$.
	By continuity, we have $\lim_{u_m \to 0}\zeta(u_m) = \zeta(0) = 0$, so $\zeta(u_m) \to 0$.

@@

\begin{lemma}\label{lem:calib-converging-regrets}
	A continuous surrogate and link $(L,\psi)$ are calibrated (via definition~\ref{def:calibrated-general}) with respect to $\ell$ if and only if, for all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
	\jessie{$(A \wedge C) \iff D$}
\end{lemma}
\begin{proof}
\jessie{$(A \wedge C) \implies D$}
	$\implies$ Take a sequence $\{u_m\}$ so that $R_L(u_m;p) \to 0$.
	Since $\zeta(0) = 0$ and $\zeta$ is continuous at $0$, $\zeta(R_L(u_m;p)) \to 0$ by calibration.
	As regret is nonnegative, we then have $R_\ell(\psi(u_m); p) \to 0$

@@

\jessie{D $\implies$ A}
	First, we can verify that $\zeta$ as constructed maps $\zeta(0) = 0$ and is continuous at $0$.	
	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, we note that $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \sup_{u' \in \Gamma(p)} (R_\ell(\psi(u'); p))$.
	If there is a $u \in \Gamma(p)$ so that $R_\ell(\psi(u); p) > \risk{\ell}(p)$, then the constant sequence $\{u_m\} = u$ for all $m$ has $R_L(u_m;p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, thus we must have $\zeta(0) = 0$.

	To see $\zeta$ is continuous at $0$, we just need to show $\lim_{c \to 0^+} \zeta(c) = 0$. 
	Fix $p \in \simplex$ and take any sequence $\{u_m\}$ so that $R_L(u_m; p) \to 0$, and therefore $R_\ell(\psi(u_m)) \to 0$.
	Since this is true for all sequences, we have the upper bound tending to $0$, and thus $\lim_{c\to 0^+}\zeta(c) = 0$.

\jessie{D $\implies$ C}
	Now, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ by construction of $\zeta$.	
	For all $u \in \reals^d$, calibration via $\zeta$ yields $R_\ell(\psi(u);p) \leq \sup_{u' : R_L(u';p) \leq R_L(u,p)} R_\ell(\psi(u') ; p)$.
	As $u$ is in the space of the supremum ($R_L(u;p) \leq R_L(u;p)$), we then have calibration by definition of the supremum.
\end{proof}
